---
title: "Meta-Analysis Course Schedule"
author: "Robert C Cline Sr"
date: "3/1/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE) 

library(readr)
library(here)
library(tidyverse)
library(metafor)
library(metaviz)
library(psychmeta)
library(easystats)


```

```{r}
options(repos = c(easystats = "https://easystats.r-universe.dev", getOption("repos")))
        
        
install.packages("easystats")#, "psychmeta", "metafor", "metaviz")
easystats::install_latest() 

install.packages("psychmeta", "metafor", "metaviz")
```


### SESSION CONTENT  

**Monday** – Classes from 2-7 PM Berlin time  
Part 1  

* Lecture: Introduction to systematic reviews and meta-analysis  
* Lecture: Effect sizes and confidence intervals  
* Exercise 1  

Part 2  

* Lecture: Sampling error and meta-analysis models  
* Lecture: Fitting meta-analysis models in R with metafor and psychmeta  
* Exercise 2        

**Tuesday** – Classes from 2-7 PM Berlin time  
Part 1  

* Lecture: Artefacts beyond sampling error: Measurement error and selection bias  
* Lecture: Moderator analysis and meta-regression  
* Exercise 3  
 
Part 2  

* Lecture: Heterogeneity in effects  
* Lecture: Presenting and interpreting meta-analysis results  
* Exercise 4   

**Wednesday** – Classes from 2-7 PM Berlin time  
Part 1  

* Lecture: Model diagnostics – assumptions, residuals, influential studies  
* Exercise 5  

Part 2   

* Lecture: Publication bias  
* Exercise 6  
  
**Thursday** – Classes from 2-7 PM Berlin time  

Part 1  

* Lecture: The systematic review process  
* Lecture: Reporting and presenting meta-analyses transparently  
* Exercise 7  

Part 2
* Refresher, Q&A, Meta-analysis reading practice

 

 